The \dealii Library, Version 9.1

### 2019-06-05 9.1/paper.tex
Correct a typo in the FE_BernardiRaugel summary

\item
  The \texttt{FE\_BernardiRaugel} class implements the non-standard
  Bernardi-Raugel (BR) element that can be used to construct a stable
  velocity-pressure pair for the Stokes equation \cite{BR85}. The BR
  element is an enriched version of the $Q_1^d$ element with added bubble
  functions on each edge (in 2d) or face (in 3d). It addresses the fact
  that the $Q_1^d\times Q_0$ combination is not inf-sup stable (requiring a
  larger velocity space), and that the $Q_2^d\times Q_1$ combination is
  stable but sub-optimal since the velocity space is too large relative to
  the pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  thus intermediate to the $Q_1^d$ and $Q_2^d$ spaces.

>>>>

\item
  The \texttt{FE\_BernardiRaugel} class implements the non-standard
  Bernardi-Raugel (BR) element that can be used to construct a stable
  velocity-pressure pair for the Stokes equation \cite{BR85}. The BR
  element is an enriched version of the $Q_1^d$ element with added bubble
  functions on each edge (in 2d) or face (in 3d). It addresses the fact
  that the $Q_1^d\times Q_0$ combination is not inf-sup stable (requiring a
  larger velocity space), and that the $Q_2^d\times Q_0$ combination is
  stable but sub-optimal since the velocity space is too large relative to
  the pressure space to provide additional accuracy commensurate with the
  cost of the large number of velocity unknowns. The BR space is
  thus intermediate to the $Q_1^d$ and $Q_2^d$ spaces.
